%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Rudra}{Sarkar}{
  \urlstyle{same}\href{http://rudrasarkar.com}{rudrasarkar.com} |
  \href{mailto:rudrasarkar311@gmail.com}{rudrasarkar311@gmail.com} |
  8967170220
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Makkaut University}
\descript{Bachelor in IT}

\location{CGPA : 8.74 }
\location{July 2024 }
\sectionsep

\subsection{PKDV}
\descript{Higher Secondary}
\location{Marks : 83.8 \% }
\location{May 2019}

\subsection{TSHS}
\descript{Secondary}
\location{Marks : 64.71 \% }
\location{May 2017}




\sectionsep

\subsection{La Martiniere for Boys}
\location{Grad. May 2011|  Kolkata, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 

Github:// \href{https://github.com/RudraSarkar5}{\bf RudraSarkar5} \\
LinkedIn://  \href{www.linkedin.com/in/rudra-sarkar-853385225}{\bf rudra-sarkar-853385225} \\




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

Full Stack Web Development in Udemy \\
PW Skills Full Stack Web Development \\

\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}


\textbullet{} \textbf{Java} \textbullet{} \textbf{Javascript} \\ \textbullet{} \textbf{Python} 
\textbullet{} \textbf{PHP}   

\textbullet{} \textbf{HTML} \textbullet{} \textbf{CSS}  \\
\textbullet{} \textbf{Node.js} \textbullet{} \textbf{RESTful APIs} \\
\textbullet{} \textbf{React.js} \textbullet{} \textbf{Redux} \\
\textbullet{} \textbf{Tailwind} \textbullet{} \textbf{Web-Socket} \\
\textbullet{} \textbf{MySQL} \textbullet{} \textbf{MongoDB} \\
\textbullet{} \textbf{Git} \textbullet{} \textbf{Chat-GPT} 

\location{Familiar:}
 \textbullet{} \textbf{Android Development}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Project}
\runsubsection{Local Store  Web App} 




\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Introducing a dynamic web application where users can seamlessly showcase their products. If a user finds interest in another's product, they can engage in real-time chats with the owner for potential purchases.
\item Frontend developed using \textbf{React.js} and enhanced with state management using \textbf{React-Redux}. \textbf{Tailwind CSS} for a sleek and responsive design.
 
\item Backend powered by \textbf{Node.js} and \textbf{Express.js}, featuring a robust \textbf{REST API} for seamless communication. Utilizes \textbf{JWT authentication} for secure user access.



\item \textbf{MongoDB} used as the database for data storage and retrieval.

\item \textbf{WebSocket} implemented for real-time chat function to enhance the user experience.
\usepackage{hyperref}

\item GitHub Repository: \href{https://github.com/RudraSarkar5/Local_Store}{\textcolor{blue}{Local Store on GitHub}}


\end{tightemize}
\sectionsep

\runsubsection{Restaurant Table Reservation System}

\begin{tightemize}
\item Introducing a user-friendly web-site for the restaurant industry. This platform empowers restaurant owners to effortlessly showcase their establishments, customize tables and  menus with prices, and enhance the overall dining experience. Customers, on the other hand, can conveniently browse listed restaurants, explore available tables, and book their preferred table for a specific date and time.

\item Entire Website developed using  \textbf{PHP} and also used \textbf{Tailwind} for responsive design.
\item  For Payment demo i used \textbf{Razorpay} and also used \textbf{PHPMailer} to make forget password functionality.
\item GitHub Repository: \href{https://github.com/RudraSarkar5/Restaurant_Booking_System_In_Php}{\textcolor{blue}{Restaurant Table Booking System on GitHub}}

\end{tightemize}
\sectionsep


\runsubsection{Tic-Tac-Toe Game (vs Computer and multiplayer)}

\begin{tightemize}
\item This game have two mode one is play against computer and other one is play against friend.
\item It's fully developed by \textbf{HTML},\textbf{CSS}and \textbf{JavaScript}.

\item Game Link:
\href{https://rudrasarkar5.github.io/tic-tac-toe/}{\textcolor{blue}{Tic-Tac-Toe Game}}

\end{tightemize}
\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Activities
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Activity}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

\item \textbf{Leetcode} Problem Solver (over 150 question solved ).
\item Daily Try to learn something about new technology.


\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     About Me
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{About Me} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

\item Location : Nabadwip,WestBengal.
\item  Language : Bengali,English,Hindi.


\end{tightemize}
\sectionsep





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file

\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
